\chapter{Acknowledgements}

First and foremost I would like to thank Björn Schäfer and Frederic Schuller for the opportunity to conduct my master thesis work as part of their respective groups. It was their support and encouragement to initiate this collaboration between our cosmology group in Heidelberg and the constructive gravity group in Erlangen that allowed me to work on a subject that deeply fascinates me. Both have significantly contributed to further increase my appreciation of relativity and the fundamental laws of nature in their unique ways, be it through the insightful discussions with Björn on his general relativity lecture material and his ability to delve to the physical root of a relativistic phenomenon (of course most are already present in Newtonian physics anyway!), or through Frederic's stringent treatment of physical theory and his constructive approach to scientific methodology that immediately resonated with me.

I also extend this gratitude to my colleagues in both groups, who spent their time in discussion with me, in particular to Max (who outperformed Mathematica), Flo (who taught me much about constructive gravity), Robert (for trading Skittles for advice) and Sven (whose hints helped me along on multiple occasions). Much of the work in this thesis was conducted alongside Max' , and with his invaluable support.

Furthermore, I wish to thank Marcus Werner for his invitation and financial support to visit him at the Yukawa Institute in Kyoto, and for the time and effort he lend me during this time. I am also most grateful for the PROMOS scholarship awarded by the DAAD that made this research visit possible.

Finally, I would like to thank Prof. Peter Fischer of Heidelberg University, who during my studies greatly supported my ambitions on numerous occasions. His encouragement and confidence in me allowed me to pursue teaching and software development projects that also contributed in great part to developing my scientific aspirations.

% CERN?
% Uni HD, interdisciplinary, TAing